The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-26 paper/main.tex
intro draft
done intro draft
starting methods. draft of method overview section
paper in proper format
change title
title change again
crummy abstract

\documentclass[sigconf]{acmart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\title{Shape Matching Element Method}

@@

@@

\input{sections/intro}
\input{sections/related}
\input{sections/results}
\input{sections/conclusion}

@@

Dump of some equations
\begin{align*}
    \mathbf{M(X)} = (X_0 - \bar{X}_0, X_1 - \bar{X}_1)\\
    \bar{\mathbf{x}} = \frac{1}{n}\sum_i^n x_i \\
    \bar{\mathbf{X}} = \frac{1}{n}\sum_i^n X_i \\
\end{align*}

>>>>

\documentclass[acmtog, anonymous,review, nonacm, balance = false]{acmart}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\input{sections/pre.tex}

@@

\title{The Shape Matching Element Method: Direct Animation of Curved Surface Models}

@@

\begin{abstract}
We introduce a new method for direct physics-based animation of volumetric curved models.  
The Shape Matching Element Method is a completely meshless approach which is robust to gaps and overlaps in geometry, 
is compatible with standard constitutive models and time  integration schemes, supports contact and frictional interactions 
as well as direct editing of simulation output. 
We demonstrate the efficacy of our algorithm by producing compelling physics-based animations from a variety of curved input models.
\end{abstract}

@@

\input{sections/intro}
\input{sections/related}
\input{sections/methods}

\input{sections/results}
\input{sections/conclusion}

@@
